---
title: "Simulation Summary Figures"
author: "Patrick Kimes"
output: 
    html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-workspace}
# Load packages and source benchmark FDR
library(tidyr)
library(dplyr)
library(ggplot2)
library(magrittr)
library(cowplot)
library(tibble)
library(ggthemes)
library(grid)
library(SummarizedBenchmark)


if(packageVersion("SummarizedBenchmark") != "0.99.2"){
  stop("Summarized Benchmark version is incorrect, please run 'devtools::install_github('areyesq89/SummarizedBenchmark', ref = 'fdrbenchmark')'.")
}
## load helper functions
for (f in list.files("../R/", "\\.(r|R)$", full.names = TRUE)) {
    source(f)
}

# set up results directory
outdir <- "../figures"
dir.create(outdir, showWarnings = FALSE)
result_summary_dir <- "./results-summary"
dir.create(result_summary_dir, showWarnings = FALSE)

gmm_results_dir <- "./results"
original_results_dir <- "./data_files"

resmet_file <- file.path(result_summary_dir, "result-metrics.rds")

resmet_gmm_file <- file.path(result_summary_dir, "gmm-result-metrics.rds")


methodset <- c("bonf", "bh", "ihw", "qvalue", "bl-df03", "lfdr",
               "fdrreg-e", "fdrreg-t", "ashq", "adapt-glm","adapt-gmm")
```

# Data Preparation

First, we load summaries for all simulations results at significance thresholds
between 0.01 and 0.10. This process can take a long time (approximately 40 minutes
per alpha cutoff) because of the large number of simulation settings that must be
read in and summarized. Ideally, this initial step should be run externally separate
from this Rmd (by default, the following code chunk will not be run).

```{r, eval = FALSE}
for (ia in 1:1) {
    summary_file <- file.path(result_summary_dir,paste0("summary_alpha", ia, ".rds"))
    if (!file.exists(summary_file)) {
        res_files <- list.files(original_results_dir, "\\.rds$", full.names = TRUE)
        res <- lapply(res_files, function(x) {
            zz <- readRDS(x)
            zz_i <- lapply(zz, `[[`, "informative")
            zz_u <- lapply(zz, `[[`, "uninformative")
            zz_i <- plotsim_standardize(zz_i, alpha = ia / 100L)
            zz_i <- dplyr::select(zz_i, rep, blabel, param.alpha, key, performanceMetric, alpha, value)
            zz_i <- dplyr::select(zz_i, rep, label, alpha, key, performanceMetric, alpha, value)
            zz_u <- plotsim_standardize(zz_u, alpha = ia / 100L)
            zz_u <- dplyr::select(zz_u, rep, blabel, param.alpha, key, performanceMetric, alpha, value)
            dplyr::full_join(zz_i, zz_u,
                             by = c("rep", "blabel", "param.alpha", "key", "performanceMetric", "alpha"),
                             suffix = c(".info", ".uninfo"))
        })
        names(res) <- gsub("\\.rds$", "", basename(res_files))
        saveRDS(res, summary_file)
    }
}
```

For new results files

```{r, eval = FALSE}
# can run this here
# alternatively, if this is too slow, can run "generate_alpha_summary.sh"
# can run this in parallel for speed increase
for (ia in 10) {
    print(ia)
  summary_file <- file.path(result_summary_dir,paste0("gmm_summary_alpha", ia, ".rds"))
    if (!file.exists(summary_file)) {
       res_files <- list.files(gmm_results_dir, "\\.rds$", full.names = TRUE)
                    
        #res_files <- list.files("results", "\\.rds$", full.names = TRresUE)
        res <- lapply(res_files, function(x) {
            cat(paste(x,"\n"))
            zz <- readRDS(x)
            zz_i <- lapply(zz, `[[`, "informative")
            zz_u <- lapply(zz, `[[`, "uninformative")
            zz_i <- plotsim_standardize(zz_i, alpha = ia / 100L)
            zz_i <- dplyr::select(zz_i, rep, label,  performanceMetric, alpha, value)
            zz_u <- plotsim_standardize(zz_u, alpha = ia / 100L)
            zz_u <- dplyr::select(zz_u, rep, label,  performanceMetric, alpha, value)
            dplyr::full_join(zz_i, zz_u,
                            by = c("rep", "label", "performanceMetric", "alpha"),
                            suffix = c(".info", ".uninfo"))
        })
        names(res) <- gsub("\\.rds$", "", basename(res_files))
        saveRDS(res, summary_file)
    }
}
```

Assuming that the summaries have been saved for all simulation settings at
the various FDR thresholds using the code above, we load the summarized results
and merge them into a single results table.

```{r}
# alphas <- 1:10
# res <- vector("list", length(alphas))
# for (ia in seq_len(length(alphas))) {
#     print(ia)
#     imethodset <- methodset
#     imethodset[which(imethodset == "ihw")] <- paste0("ihw-a", sprintf("%02d", alphas[ia]))
#     ires <- readRDS(file.path(result_summary_dir, paste0("gmm_summary_alpha", alphas[ia], ".rds")))
#     ires <- bind_rows(ires, .id = "setting")
#     ires <- dplyr::mutate(ires, dist = gsub(".*?-benchmark-(.*)", "\\1", setting),
#                          setting = gsub("(.*?)-benchmark-.*", "\\1", setting))
#     ires <- dplyr::filter(ires, blabel %in% imethodset)
#     ires <- dplyr::mutate(ires, blabel = gsub("(-a)(.*)", "", blabel))
#     res[[ia]] <- ires
# }
# res <- bind_rows(res)
# res <- dplyr::select(res, -param.alpha)
# res <- dplyr::rename(res, Method = blabel)
# res <- dplyr::mutate(res, Method = gsub("-df03", "", Method))
# #res <- dplyr::mutate(res, Method = factor(Method, levels = gsub("-df03", "", methodset)))
```

Run this for add new methods
```{r}
alphas <- 1:10
gmm_res <- vector("list", length(alphas))
gmmmethodset <- c("AdaPTGMM")
for (ia in seq_len(length(alphas))) {
    print(ia)
    full_methodset <- c(methodset,gmmmethodset)
    ires <-  readRDS(file.path(result_summary_dir, paste0("gmm_summary_alpha", alphas[ia], ".rds")))
    ires <- bind_rows(ires, .id = "setting")
    ires <- dplyr::mutate(ires, dist = gsub(".*?-benchmark-(.*)", "\\1", setting),
                         setting = gsub("(.*?)-benchmark-.*", "\\1", setting))
    ires <- dplyr::filter(ires, label %in% full_methodset)
    ires <- dplyr::mutate(ires, label = gsub("(-a)(.*)", "", label))
    gmm_res[[ia]] <- ires
}
gmm_res <- bind_rows(gmm_res)
gmm_res <- dplyr::rename(gmm_res, Method = label)
gmm_res <- dplyr::mutate(gmm_res, Method = gsub("-df03", "", Method))
#gmm_res <- dplyr::mutate(gmm_res, Method = factor(Method, levels = gsub("-df03", "", methodset)))
``` 
 



# Augmented version Patrick
```{r}

resmet <- dplyr::mutate(gmm_res, value.info = ifelse(is.na(value.info), 0, value.info),
                        value.uninfo = ifelse(is.na(value.uninfo), 0, value.uninfo))
resmet <- dplyr::group_by(resmet, setting, dist, Method, performanceMetric, alpha)
resmet <- dplyr::summarize(resmet,
                           mean.info = mean(value.info, na.rm = TRUE),
                           se.info = sd(value.info, na.rm = TRUE) / sqrt(sum(!is.na(value.info))),
                           nNA.info = sum(is.na(value.info)),
                           mean.diff = mean(value.info - value.uninfo, na.rm = TRUE),
                           se.diff = sd(value.info - value.uninfo, na.rm = TRUE) /
                               sqrt(sum(!is.na(value.info - value.uninfo))))
resmet <- dplyr::ungroup(resmet)

resmet <- dplyr::mutate(resmet, inform = ifelse(grepl("varyinginfo", setting), dist, NA))
resmet <- dplyr::mutate(resmet, inform = as.numeric(gsub("level", "", inform)))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("varyinginfo", setting), "gaussian", dist))

resmet <- dplyr::mutate(resmet, pi0 = ifelse(grepl("varyingpi0", setting), dist, 90))
resmet <- dplyr::mutate(resmet, pi0 = as.numeric(gsub("nullprop", "", pi0)))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyingpi0$", setting), "gaussian", dist))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyingpi0-t$", setting), "t11", dist))

resmet <- dplyr::mutate(resmet, signal = ifelse(grepl("uasettings", setting), dist, NA))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^uasettings$", setting), "gaussian", dist))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^uasettings-t$", setting), "t11", dist))
resmet <- dplyr::mutate(resmet, setting = ifelse(grepl("uasettings", setting), "uasettings", setting))

resmet <- dplyr::mutate(resmet, pi0 = ifelse(grepl("varyingntests", setting), 90, pi0))
resmet <- dplyr::mutate(resmet, ntests = ifelse(grepl("varyingntests", setting), dist, "n20000"))
resmet <- dplyr::mutate(resmet, ntests = as.numeric(gsub("n", "", ntests)))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("varyingntests", setting), "gaussian", dist))


resmet <- dplyr::mutate(resmet, dist = factor(dist, levels = c("gaussian", "t11", "t5", "chisq4"),
                                              labels = c(expression("Distribution: " * N(0, 1)),
                                                         expression("Distribution: " * t[11]),
                                                         expression("Distribution: " * t[5]),
                                                         expression("Distribution: " * {chi^2}[4]))))


resmet <- dplyr::filter(resmet, !( grepl("chi", dist) & Method == "ashq" ))
resmet <- dplyr::filter(resmet, !( grepl("chi", dist) & grepl("fdrreg", Method) ))


resmet_file <- file.path(result_summary_dir, "gmm-result-metrics.rds")

saveRDS(resmet, file = resmet_file)

```
